---
title: "Prediction for Fleet 2,3,4"
output: html_document
date: "2023-12-03"
---
```{r}
model_2 <- readRDS("tuned_model_for_fleet_2.rds")
summary(model_2)
```
Interpretation of the model:

call: This shows the function call used to create the random forest model. It provides information about the parameters and settings used in creating the model.

type: This indicates the type of model. In this case, it's a character indicating the type of the model. You might want to check if it says something like "randomForest" to confirm that it's a random forest model.

predicted: This likely contains the predicted values generated by the model. Each of the 178,008 values corresponds to a prediction for each observation in your dataset.

mse (Mean Squared Error): This is a measure of the average squared difference between the observed and predicted values. A lower MSE indicates better model performance.

rsq (R-squared): R-squared is a measure of how well the model explains the variability in the response variable. A value of 100 indicates a perfect fit, but be cautious as extremely high R-squared values may suggest overfitting.

oob.times: Out-of-bag (OOB) error estimates for each observation. The OOB error is an estimate of how well the model generalizes to new, unseen data.

importance: Variable importance scores for each predictor variable. Higher values suggest more important variables in predicting the response.

ntree: The number of trees in the random forest. In this case, there is one tree.

mtry: The number of variables randomly sampled as candidates at each split. In this case, there is one variable.

forest: A list containing information about each tree in the forest. In this case, there are 11 elements in the list, possibly representing information about 11 trees.

y: The response variable values. There are 178,008 values, corresponding to the response variable in your dataset.

terms: This indicates the terms used in the model. It says there are 3 terms, and it's of type "call". This might be related to the formula you used to specify the model.
```{r}
model_3 <- readRDS("tuned_model_for_fleet_3.rds")
summary(model_3)
```
Interpretation of the model:
call: This shows the function call used to create the random forest model. It provides information about the parameters and settings used in creating the model.

type: This indicates the type of model. In this case, it's a character indicating the type of the model. You might want to check if it says something like "randomForest" to confirm that it's a random forest model.

predicted: This likely contains the predicted values generated by the model. Each of the 43,714 values corresponds to a prediction for each observation in your dataset.

mse (Mean Squared Error): This is a measure of the average squared difference between the observed and predicted values. A lower MSE indicates better model performance.

rsq (R-squared): R-squared is a measure of how well the model explains the variability in the response variable. A value of 100 indicates a perfect fit, but be cautious as extremely high R-squared values may suggest overfitting.

oob.times: Out-of-bag (OOB) error estimates for each observation. The OOB error is an estimate of how well the model generalizes to new, unseen data.

importance: Variable importance scores for each predictor variable. Higher values suggest more important variables in predicting the response.

ntree: The number of trees in the random forest. In this case, there is one tree.

mtry: The number of variables randomly sampled as candidates at each split. In this case, there is one variable.

forest: A list containing information about each tree in the forest. In this case, there are 11 elements in the list, possibly representing information about 11 trees.

y: The response variable values. There are 43,714 values, corresponding to the response variable in your dataset.

terms: This indicates the terms used in the model. It says there are 3 terms, and it's of type "call". This might be related to the formula you used to specify the model.
```{r}
model_4 <- readRDS("tuned_model_for_fleet_4.rds")
summary(model_4)
```
call: This shows the function call used to create the random forest model. It provides information about the parameters and settings used in creating the model.

type: This indicates the type of model. In this case, it's a character indicating the type of the model.

predicted: This likely contains the predicted values generated by the model. Each of the 43,712 values corresponds to a prediction for each observation in your dataset.

mse (Mean Squared Error): This is a measure of the average squared difference between the observed and predicted values. A lower MSE indicates better model performance.

rsq (R-squared): R-squared is a measure of how well the model explains the variability in the response variable. A value of 500 might be unusual, as R-squared values typically range from 0 to 1. Please check if this value is accurate.

oob.times: Out-of-bag (OOB) error estimates for each observation. The OOB error is an estimate of how well the model generalizes to new, unseen data.

importance: Variable importance scores for each predictor variable. Higher values suggest more important variables in predicting the response.

ntree: The number of trees in the random forest. In this case, there is one tree.

mtry: The number of variables randomly sampled as candidates at each split. In this case, there is one variable.

forest: A list containing information about each tree in the forest. In this case, there are 11 elements in the list, possibly representing information about 11 trees.

y: The response variable values. There are 43,712 values, corresponding to the response variable in your dataset.

xNames: The names of the predictor variables used in the model. There are 12 predictor variables.

problemType: The type of problem the model is solving. It is indicated as "character."

tuneValue: Information related to tuning parameters during model training. It's a data.frame.

obsLevels: Logical indicating whether observed levels of the response variable were included.

param: A list containing information about additional parameters.
```{r}
df2=read.csv("Fleet_prediction_data_fleet_2.csv")
df3=read.csv("Fleet_prediction_data_fleet_3.csv")
df4=read.csv("Fleet_prediction_data_fleet_4.csv")
```
```{r}
str(df2)
str(df3)
str(df4)
```
```{r}
df2$X <- NULL
df2$Unnamed..0<-NULL
df2$label<-NULL
df2$distance_from_1<-NULL
df2$Time<-NULL
df2$Air_Flow_Rate_from_Mass_Flow_Sensor_g_s<-NULL
str(df2)
df3$X <- NULL
df3$Unnamed..0<-NULL
df3$label<-NULL
df3$distance_from_1<-NULL
df3$Time<-NULL
df3$Air_Flow_Rate_from_Mass_Flow_Sensor_g_s<-NULL
str(df3)
df4$X <- NULL
df4$Unnamed..0<-NULL
df4$label<-NULL
df4$distance_from_1<-NULL
df4$Time<-NULL
df4$Air_Flow_Rate_from_Mass_Flow_Sensor_g_s<-NULL
str(df4)
```
```{r}
library(randomForest)
Air_Flow_Rate_from_Mass_Flow_Sensor_g_s_2 <- predict(model_2, newdata = df2)
print(Air_Flow_Rate_from_Mass_Flow_Sensor_g_s_2)
```
```{r}
Air_Flow_Rate_from_Mass_Flow_Sensor_g_s_3 <- predict(model_3, newdata = df3)
print(Air_Flow_Rate_from_Mass_Flow_Sensor_g_s_3)
```




